Colonies - Compute Continuums across Platforms

### 2023-05-02 paper_2023/paper.tex
wip

\section{Discussion}
This paper has presented an open-source framework called Colonies, which is designed to streamline execution of computational workloads across platforms. Colonies provides a \emph{distributed runtime environment}, called a \emph{Colony}, which serves as an intermediary layer to indirectly control and integrate with other computer systems. Instead of directly connecting different systems together, Colonies allows services or users to publish instructions and then assign these instructions to other services. By chaining instructions together, it becomes possible to execute workloads that can operate seamlessly across different platforms.

Unlike many other systems where security sometimes is added later on, Colonies builds on the principle: \emph{security first}. Public key encryption allows administrators and users to maintain strict control over a colony, even when executors are dispersed throughout the Internet. Each colony is governed by a private key that serves as a central authority, analogous to \emph{one ring to rule them all}, making it possible to control a colony as if it was a single machine. The zero-trust principle, \emph{trust, but verify} also enables development of immune system-like functionality where malfunctional executors can be excluded and replaced with fresh new ones, ensuring that the overall performance and reliability of the system is not compromised.

@@

It has been mentioned in the paper several times that Colonies is designed to simplify integration with other systems, but what feature in Colonies makes integration easier? Microservices is a design principle used by Colonies to simplify integration. As executors are designed to be loosely-coupled microservices, the entire system becomes easier to develop, test, and maintain. For example, different teams can take on responsibility to develop a certain executor, which can then be used as a part of complex workflows running across platforms. By designing each executor as a standalone microservice, it also becomes easy to scale the system by simply deploying more executors. This also opens up for an intriguing possibility to delegate colony management responsibility to a software agent that can automatically provision and deploy executors on demand.

>>>>

\section{Discussion}
This paper has presented an open-source framework called Colonies designed to streamline execution of computational workloads across platforms. Colonies provides a \emph{distributed runtime environment}, called a \emph{Colony}, which serves as an intermediary layer to indirectly control other computer systems. Instead of directly connecting different systems together, Colonies allows services or users to publish instructions and then assign these instructions to other services. By chaining instructions together, it becomes possible to execute workloads that can operate seamlessly across different platforms.

Colonies builds on the principle: \emph{security first}. Public key encryption allows administrators and users to maintain strict control over a colony, even when executors are dispersed throughout the Internet. Each colony is governed by a private key that serves as a central authority, analogous to \emph{one ring to rule them all}, making it possible to control a colony as if it was a single machine. The zero-trust principle, \emph{trust, but verify} also enables development of immune system-like functionality where malfunctional executors can be excluded and replaced with fresh new ones, ensuring that the overall performance and reliability of the system is not compromised.

@@

It has been mentioned in the paper several times that Colonies is designed to simplify integration with other systems. Microservices is a design principle used by Colonies to simplify integration. As executors are designed to be loosely-coupled microservices, the entire system becomes easier to develop, test, and maintain. For example, different teams can take on responsibility to develop a certain executor, which can then be used as a part of complex workflows running across platforms. By designing each executor as a standalone microservice, it also becomes easy to scale the system by simply deploying more executors. This also opens up for an intriguing possibility to delegate colony management responsibility to a software agent that can automatically provision and deploy executors on demand.
